Parsing Postfix log files

### 2007-11-13 doc/logparser-acronyms.tex
More corrections.
Corrections to Coverage, Limitations and Review of Other Parsers.
Finished the corrections, or marked where corrections remain to be made. More acronyms, and updated acronyms I missed earlier.

\newacronym{API}{Application Programming Interface}{description={
    One of the fundamental concepts when writing programs is the reuse of
    existing code, so that each program does not reinvent the wheel.  When
    a body of code is intended to be reused repeatedly, the user of this
    code needs to be informed of the functionality provided by the code.
    An API defines the interface provided to the user, and acts a contract
    between the user and the provider: if the user adheres to the API the
    provider guarantees it will work, while the provider is free to change
    the implementation as long as the API is preserved.
}}

@@

\newacronym{FQDN}{Fully Qualified Domain Name}{description={
    An FQDN is a hostname plus domain name, e.g.
        example.com     is a domain name    \newline
        www             is a hostname       \newline
        www.example.com is a FQDN
}}

@@

\newacronym{regexs}{Regular Expressions}{description={
    Regular expressions are a method of matching patterns in text that are
    explained in detail in~\cite{wikipedia-regex, perlre} .
}}

>>>>

\newacronym{API}{Application Programming Interface}{description={
    One of the fundamental concepts when writing programs is the reuse of
    existing code, so that each program does not reinvent the wheel.  When
    a body of code is intended to be reused repeatedly, the user of this
    code needs to be informed of the functionality provided by the code.
    An API defines the interface provided to the user, and acts as a
    contract between the user and the provider: if the user adheres to the
    API the provider guarantees it will work, while the provider is free to
    change the implementation as long as the API is preserved.
}}

@@

\newacronym{FQDN}{Fully Qualified Domain Name}{description={
    An FQDN is a hostname plus domain name, e.g.    \newline
        example.com     is a domain name          \newline
        www             is a hostname             \newline
        www.example.com is a FQDN
}}

@@

% I think this is better than having both regex and regexs in the acronym
% list.
\newcommand{\regexs}{\regex{}s}

\newacronym{ESMTP}{Extended SMTP}{description={
    ESMTP is Extended SMTP, defined in RFC~1869~\cite{RFC1869}.
}}

\newacronym{HTML}{Hypertext Markup Language}{description={
    HTML is the markup language designed for writing web
    pages~\cite{wikipedia-html, w3schools-html}.
}}

\newacronym{IP}{Internet Protocol}{description={
    XXX ADD A DEFINITION\@.
}}
